\documentclass{article}
\usepackage[utf8]{inputenc}
\title{Blog Analysis System}
\author{RoshaanT1}
\date{\today}

\begin{document}
\maketitle

\section{Project Overview}
This document provides a condensed analysis of the Blog Analysis System, focusing on essential components such as project overview, requirements analysis, core implementation, technology stack, and deliverables.

\section{Requirements Analysis}
The system is designed to analyze blog content for readability, SEO, and engagement metrics. Key requirements include:
\begin{itemize}
  \item Ability to parse and analyze blog posts.
  \item Metrics for readability and SEO performance.
  \item Reporting tools for engagement metrics.
\end{itemize}

\section{Core Implementation}
The core implementation consists of the following components:
\begin{itemize}
  \item \textbf{Parser:} Extracts content from blog posts.
  \item \textbf{Analyzer:} Evaluates readability and SEO metrics.
  \item \textbf{Reporter:} Generates reports based on analysis.
\end{itemize}

\section{Technology Stack}
The system leverages the following technologies:
\begin{itemize}
  \item \textbf{Programming Language:} Python 3
  \item \textbf{Libraries:} BeautifulSoup for parsing, TextBlob for readability analysis, and Matplotlib for reporting.
  \item \textbf{Database:} SQLite for storing analyzed data.
\end{itemize}

\section{Deliverables}
The final deliverables include:
\begin{itemize}
  \item A fully functional Blog Analysis System.
  \item Documentation outlining the implementation and usage.
  \item A user manual for end-users.
\end{itemize}

\end{document}